### 2020-10-25 Thesis-Chapter3-PolicyMaking.tex
Termify argument maps and remove strategy notes
Introduce OODA loop

\subsection{Lessons}

@@

Rittel's follow-up research offers another tool: argument mapping.

% - Avoid pitfalls of
%   - Easy answers
%     - EA mandates, complexity denial
%   - Fallacies!
%   - Bad results with long technical tails

% Note: a problem with muddling through wicked problems is that each attempted fix leads to long lasting unintended side
% effects. This is especially true with matters of encryption, where the data could be stored for years till it can be
% decrypted! So must be very careful to avoid solution attempts that leave long scars.

\section{Proposal: The OODA Loop for Policymaking}

\ac{OODAloop}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-loop.png}
    \caption[The OODA Loop]{The OODA Loop}
    \label{fig-ooda-loop}
\end{figure}

% commission_tackling_2018:
% - Strategies
%   - Authoritative
%   - Competitive
%   - Collaborative
% - Approaches
%   - Linear problem solving
%     - Ineffective! Several reasons, good breakdown. Dovetails with rozenshtein_wicked_2018.
%   - Holistic problem solving: adaptive, innovative, flexible, cross-organizational
% - Avoid
%   - Narrow solutions

% rozenshtein_wicked_2018:
% - Approaches
  % - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  % - Risk management (--finally, something familiar to security experts!)
  %   - So, a broader view of security, inclusive of both public safety and information security
  %   - In this model, threat actors now include terrorists, CSAM distributors, organized crime
  %     - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
  %         identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
  %         be useful.
  %   - I have already suggested adding government mandates to the traditional IS threat model
  % - Imperfect solutions, like lawful hacking
  % - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
  %     commission_tackling_2018)
% - Avoid
%   - Easy answers ("narrow solutions" from commission_tackling_2018)
%     - Such as EA mandates or "golden age of surveillance"-based denials

% matyas_incommensurability_2018:
% - Approaches to reducing incommensurability
%   - Reduce gray area between rules and principles (i.e. keep laws up to date with technology)
  % - Use transparency and accountability (through technical means)

% feeley_judicial_2000:
% - Classical analytic method ("linear" in commission_tackling_2018)
% % 1. Classical analytic method; each step has its own approaches, e.g. cost-benefit analysis (loosely based on natural
% % sciences)
% %   (missing: Observe)
% %   a. Define the problem (Orient)
% %   b. Identify a goal (Orient)
% %   c. Generate a range of alternatives for achieving that goal (Orient)
% %   d. Select the alternative that seems most promising (Decide)
% %   e. Implement the selected alternative (Act)
% %   (missing: loop)
% - Incremental intuitive decision making ("Muddling through" in rozenshtein_wicked_2018)
% - The hermeneutic circle

% How to tackle wicked problems in general? Take some tips from commission_tackling_2018, rozenshtein_wicked_2018,
% feeley_judicial_2000, and matyas_incommensurability_2018:
% Correctly state the problem--identify the root causes. They aren't going away, there by definition is no clear long
% term solution. Put the proposed solutions in context--none are perfect, none are permanent. For EA in particular,
% consider balance of principles and rules.

>>>>

\subsection{Lessons}
\label{sec-policy-lessons}

@@

\section{Proposal: The OODA Loop for Wicked Problems}

The above discussion describes the failure of well-established methods of policymaking at addressing \acp{wicked-prob}
and properties a better method would have. Here, I propose a modified \acs{OODAloop} as an alternative policymaking
model.

The \ac{OODAloop} was a developed by Air Force Colonel John Boyd in the context of military strategy, but its ideas have
penetrated many other sectors \cite{angerman_2004}. Boyd created it as a description of a successful strategy for
countering opponents in real-time combat. There is an emphasis on speed and ``getting inside'' your opponent's loop. It
is illustrated in \myfig{fig-ooda-loop}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-vanilla.png}
    \caption[The OODA Loop]{The OODA Loop}
    \label{fig-ooda-loop}
\end{figure}

The \ac{OODAloop} serves as a good basis for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action, but it emphasizes the \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking doesn't share the pace of real-time combat, in other ways the metaphor holds up. This
is the idea behind language like the ``war on drugs''---whether combating armed opponents or \acp{wicked-prob}, one is
contending with an unpredictable opponent in an environment lacking complete information with an unlimited set of
possible actions.

The \ac{OODAloop} as is does not have all the properties listed in \mysec{sec-policy-lessons}, however.
... %TODO: finish this
See \myfig{fig-policy-ooda-loop}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-loop.png}
    \caption[The OODA Loop for Wicked Problems]{The OODA Loop for Wicked Problems}
    \label{fig-policy-ooda-loop}
\end{figure}
